---
title: "Vignette_TCGA_DIVSA"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette_TCGA_DIVSA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TCGA.DIVSA)

```

First you must access available TCGA data table.

```{r data}
system.file("extdata", "tcga_cdr.tsv", package = "TCGA.DIVSA")

file <- system.file("extdata", "tcga_cdr.tsv", package = "TCGA.DIVSA")

```

The general command to create both the boxplot and statistical comparison is shown below:

divsa(table,phenotype,cancer_type,patient,meta_lev1,meta_lev2,meta_col)

The cancer_type and patient arguments are exclusive, both can not be provided at the same time.

The command below will show a boxplot and print Wilcox statistical comparison test of age_at_initial_pathologic_diagnosis in patients with ACC and BRCA cancers at stages II and III of ajcc_pathologic_tumor_stage.

```{r command}
divsa(table=file,phenotype='age_at_initial_pathologic_diagnosis',cancer_type=c("ACC","BRCA"),meta_lev1="Stage II",meta_lev2="Stage III",meta_col='ajcc_pathologic_tumor_stage')

```
